### 2023-11-30 state/rnn.tex
Worked on paper+corrected errors
Changed a bunch of files
Added almost all symbols

\section{\acs{RNN}}\label{sec:rnn}

@@

\begin{equation}\label{eq:rnn}
  \overrightarrow{h_t}=f(\overrightarrow{x_t},\overrightarrow{h_{t-1}})
\end{equation}

The hidden state ($\overrightarrow{h_t}$) carries all the past informations for the next time step. It also serves as the output of the \ac{RNN}.

They are trained the same way \ac{NN} are, measuring the error, backpropagate and adjust the weights accordingly.

\subsection{Simple \ac{RNN}}

@@

\begin{equation}\label{eq:srnn}
  \overrightarrow{h_t}=tanh([\overrightarrow{x_t},\overrightarrow{h_{t-1}}]\cdot w + b)
\end{equation}

Where $t\in\mathbb{N}^*$ is the time index, $w$ the weight matrix, $b$ the bias matrix, $\overrightarrow{x_t}$ the input vector and $\overrightarrow{h_{t}}$ the hidden state of the \ac{RNN}.

>>>>

\section{\acl{RNN}}\label{sec:rnn}

@@

\begin{equation}\label{eq:rnn}
  \symvh_t=f(\symvx_t,\symvh_{t-1})
\end{equation}

The hidden state ($\symvh_t$) carries all the past informations for the next time step. It also serves as the output of the \ac{RNN}.

They are trained the same way \ac{NN} are, measuring the error, backpropagating and adjusting the weights accordingly.

\subsection{Simple \acl{RNN}}

@@

\begin{equation}\label{eq:srnn}
  \symvh_t=tanh([\symvx_t,\symvh_{t-1}]\cdot \symmw + \symvb)
\end{equation}

Where $t\in\mathbb{N}^*$ is the time index, \symmw the weight matrix, \symvb the bias vector, \symvx the input vector and \symvh the hidden state of the \ac{RNN}.
